Optimal (Multiway) Spatial Joins

### 2024-05-28 4.2.tex
4.2

First, we prove (1).

Next, we prove (2).

Finally, we prove (3).

>>>>

First, we prove (1). By the definition of $\dcross_H(\bm{t})$ and $\dcross_V(\bm{t})$, $h$ and $v$ crosses $B_\bm{t}$. Thus, the intersection of $h$ and $v$ is a point in $B_\bm{t}$. Since $B_\bm{t}$ is the intersection of $\bm{t}[1],...,\bm{t}[k-2]$, the intersection of $h$ and $v$ lies in all the rectangles $r_1,...,r_{k-2}$. Therefore, $h\cap v\bigcap_{i = 1}^{k-2}r_i \neq \emptyset$, and  the tuple $(r_1,...,r_{k-2},h,v)$ is a result tuple in $\J(R_1,...,R_{k-2},H,V)$.

Next, we prove (2). Since $(r_1,...,r_{k-2},h,v)\in \J_1$, both $h$
 and $v$ cross the rectangles $r_1,...,r_{k-2}$. Hence, for $i\in[k-2]$, the y-coorninate of $h$ is in the range $[\ybot(r_i'), \ytop(r_i')]$ and the x-coordinate of $v$ is in $[\xleft(r_i'), \xright(\xright(r_i'))]$.
Finally, we prove (3).
